---
title: "BABS Neuropsych Summary"
author: "JLC"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---
# Brandeis Aging Brain Study (BABS) Neuropsych Battery: Descriptive Summary

```{r setup, warning=FALSE, message=FALSE}
rm(list=ls())

# Packages
library(knitr); library(kableExtra); library(RColorBrewer); library(correlation); library(readxl); library(psych); library(ds4psy); library(tidyverse)

#Create data directories
NP.path<-"/Volumes/berry-lab/berry-lab/Brandeis_Aging_Brain_Study/BABS Data/Analysis/BABS_Neuropsych_Data_Validated.csv"
subj.path <-"/Volumes/berry-lab/berry-lab/Brandeis_Aging_Brain_Study/BABS Data/"

#Make data frames for neuropsych battery items from excel spreadsheet
BABS.NP.sess1 <- read.csv(NP.path, header = T)

#Make data frame for NIH toolbox data
sub.IDs <- c("BABS178","BABS182","BABS184","BABS186","BABS187","BABS188","BABS189","BABS190","BABS191","BABS192",
             "BABS193","BABS194","BABS195","BABS197","BABS198","BABS199","BABS200","BABS201","BABS203","BABS204",
             "BABS207","BABS208","BABS209","BABS210","BABS212","BABS213","BABS214","BABS215","BABS216","BABS217",
             "BABS218","BABS219","BABS220","BABS221","BABS222","BABS223","BABS224","BABS225","BABS226","BABS227",
             "BABS228","BABS229","BABS230","BABS231","BABS232","BABS232","BABS233","BABS234","BABS235","BABS236",
             "BABS237","BABS238","BABS239","BABS240","BABS241","BABS242","BABS243","BABS244","BABS245","BABS246",
             "BABS247","BABS248","BABS249","BABS251","BABS252","BABS253","BABS254","BABS255","BABS256","BABS257",
             "BABS258","BABS259","BABS260","BABS261","BABS262","BABS263","BABS264","BABS265","BABS267","BABS268",
             "BABS270","BABS271","BABS274","BABS275","BABS276","BABS277","BABS278","BABS280","BABS281","BABS282",
             "BABS283","BABS285","BABS287","BABS289","BABS212","BABS290","BABS291","BABS293","BABS294","BABS295",
             "BABS297","BABS298","BABS299","BABS300","BABS301","BABS302","BABS304","BABS305","BABS310")
NIH.toolbox.path <- data_frame()
for (sid in 1:length(sub.IDs)) {   
      NIH.fname <- paste0(subj.path, sub.IDs[sid], "/Session_1/NIH_TOOLBOX/");
      file <- dir(NIH.fname, pattern = "*Structure Assessment Scores.csv");
      setwd(NIH.fname);
      file_data <- read_csv(file, col_types = "c");
NIH.toolbox.path <- bind_rows(NIH.toolbox.path, file_data);
}
#need to clean up variable entry of subject IDs
d.NIH <- NIH.toolbox.path %>%
  mutate(ID = parse_number(NIH.toolbox.path$PIN),
         BABS_ID = (paste0("BABS",ID)))
```

# Behavioral Measures {.tabset}
## General Cognitive Function {.tabset}

### MMSE

```{r MMSE, warning=FALSE, message=FALSE}
#creating data frame with relevant variables
d.MMSE <- BABS.NP.sess1 %>% select(BABS_ID, MMSE) %>% distinct(BABS_ID, .keep_all = T) %>%
    mutate_at(vars(starts_with("MMSE")), as.numeric)
#counting the number of observations and summarizing mean & SD
MMSE.sum <- d.MMSE %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*")

kable(MMSE.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "MMSE Summary Table") %>% kable_styling()
#plotting distribution of scores
p.MMSE <- ggplot(d.MMSE, aes(MMSE)) +
  geom_bar() + scale_x_continuous(limits = c(20,31), breaks = seq(20,30,1)) +
  labs(title = "MMSE Scores in BABS Sample") +
  theme_classic()
p.MMSE
```

## Working Memory {.tabset}
### Digit Span
#### Forward

```{r DigSpan_for, warning=FALSE, message=FALSE}
#creating data frame with relevant variables
d.DigSpan.F <- BABS.NP.sess1 %>% select(BABS_ID, DigitSpan_Forward) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
    mutate_at(vars(starts_with("Digit")), as.numeric)
#counting the number of observations and summarizing mean & SD
DigSpan.F.sum <- d.DigSpan.F %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*")

kable(DigSpan.F.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "Forward Digit Span Summary Table") %>% kable_styling()
#plotting distribution of scores
p.DigSpan.F <- ggplot(d.DigSpan.F, aes(DigitSpan_Forward)) +
  geom_bar() + scale_x_continuous(limits = c(2,15), breaks = seq(2,14,1)) +
  labs(title = "Forward Digit Span Scores in BABS Sample") +
  theme_classic()
p.DigSpan.F
```

#### Backward

```{r DigSpan_back, warning=FALSE, message=FALSE}
#creating data frame with relevant variables
d.DigSpan.B <- BABS.NP.sess1 %>% select(BABS_ID, DigitSpan_Backward) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("Digit")), as.numeric)
#counting the number of observations and summarizing mean & SD
DigSpan.B.sum <- d.DigSpan.B %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*")

kable(DigSpan.B.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "Backward Digit Span Summary Table") %>% kable_styling()
#plotting distribution of scores
p.DigSpan.B <- ggplot(d.DigSpan.B, aes(DigitSpan_Backward)) +
  geom_bar() + scale_x_continuous(limits = c(2,15), breaks = seq(2,14,1)) +
  labs(title = "Backward Digit Span Scores in BABS Sample") +
  theme_classic()
p.DigSpan.B
```

### Keep Track Task

```{r KeepTrack, warning=FALSE, message=FALSE}
#creating data frame with relevant variables
d.KeepTrack <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("KEEP"), THREECATEGORIES_TOTAL) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(ends_with("TOTAL")), as.numeric)
#counting the number of observations and summarizing mean & SD
KeepTrack.sum <- d.KeepTrack %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(KeepTrack.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "Keep Track Summary Table") %>% kable_styling()
#creating long data frame
d.KeepTrack.long <- d.KeepTrack %>% 
  pivot_longer(names_to = "Level", values_to = "Score", -c(BABS_ID, `AGE AT SESSION`, KEEPTRACK_DIFFICULTY_LEVEL))
d.KeepTrack.long$Level <- factor(d.KeepTrack.long$Level, levels = c("KEEPTRACK_ONECATEGORY_TOTAL","KEEPTRACK_TWOCATEGORIES_TOTAL","THREECATEGORIES_TOTAL", "KEEPTRACK_FOURCATEGORIES_TOTAL"), labels = c(1,2,3,4))
#plotting distribution of scores
p.KeepTrack <- ggplot(d.KeepTrack.long, aes(Score)) +
  geom_bar() + 
  labs(title = "Keep Track Scores in BABS Sample") +
  theme_classic() + facet_grid(.~Level)
p.KeepTrack
```

### Spatial N-Back

```{r NBack, warning=FALSE, message=FALSE}
#creating data frame with relevant variables
d.NBack <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("NBACK")) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
    mutate_at(vars(ends_with("BACK")), as.numeric)
#counting the number of observations and summarizing mean & SD
Nback.sum <- d.NBack %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(Nback.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "Spatial N-Back Summary Table") %>% kable_styling()
#creating long data frame
d.Nback.long <- d.NBack %>% 
  pivot_longer(names_to = "Level", values_to = "Score", -c(BABS_ID, `AGE AT SESSION`, NBACK_VERSION, NBACK_DIFFICULTY_LEVEL))
d.Nback.long$Level <- factor(d.Nback.long$Level, levels = c("NBACK_ONEBACK","NBACK_TWOBACK"), 
                                 labels = c(1,2))
#plotting distribution of scores
p.Nback <- ggplot(d.Nback.long, aes(Score)) +
  geom_bar() + 
  labs(title = "N-Back Scores in BABS Sample") +
  theme_classic() + facet_grid(.~Level)
p.Nback

#adding a new variable for ease of plotting
Nback.sum$Level <- factor(Nback.sum$Variable, levels = c("NBACK_ONEBACK", "NBACK_TWOBACK"), labels = c(1,2))
d.Nback.long$mean <- d.Nback.long$Score
fig.Nback.lines <- ggplot(Nback.sum %>% filter(Level == 1 | Level == 2), aes(x=Level, y=mean)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), axis.title.y = element_text(face="bold", size=16),legend.title = element_text(face="bold", size=16)) +
  geom_bar(stat="identity", position=position_dodge(), alpha=.45, size=1.5) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=mean-se, ymax=mean+se), width=.2, size=1.25) +  
  geom_point(data = d.Nback.long, aes(x=Level, y=mean),
             stat="identity", alpha=0.7) +
  geom_line(data = d.Nback.long, aes(x=Level, y=mean, group=BABS_ID, colour = factor(BABS_ID)), alpha = .5) +
  xlab("N-Back Level") + ylab("Percent Correct")
fig.Nback <- fig.Nback.lines + guides(colour=FALSE)
fig.Nback
```

## Inhibition {.tabset}
### Stroop (Paper version)

```{r Stroop_paper, warning=FALSE, message=FALSE}
#creating data frame with relevant variables
d.Stroop.paper <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("STROOP")) %>%
  select(-STROOP_INCONG_MINUS_CONG_CORR) %>% distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("STROOP")), as.numeric)
  
Stroop.paper.sum <- d.Stroop.paper %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(Stroop.paper.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "Stroop Paper Summary Table") %>% kable_styling()

#plotting summary of scores across condition
##changing variable name for ease of plotting
Stroop.paper.sum$Variable <- factor(Stroop.paper.sum$Variable, levels = c("STROOP_WORD_CORRECT", "STROOP_COLOR_CORRECT", "STROOP_COLORWORD_CORRECT", "STROOP_WORD_INCORRECT", "STROOP_COLOR_INCORRECT", "STROOP_COLORWORD_INCORRECT"), labels = c("Word-Correct", "Color-Correct", "ColorWord-Correct", "Word-Incorrect","Color-Incorrect","ColorWord-Incorrect"))
p.Stroop.paper <- ggplot(Stroop.paper.sum, aes(x=Variable, y=mean)) +
  geom_bar(stat="identity", position=position_dodge(), alpha=.45, size=1.5) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=mean-se, ymax=mean+se), width=.2, size=1.25) + 
  labs(title = "Stroop (Paper: Items in 45s interval) in BABS Sample") +
  theme_classic()
p.Stroop.paper
```

### Stroop (Computer version)

```{r Stroop_comp, warning=FALSE, message=FALSE}
#creating data frame with relevant variables
d.Stroop.comp <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, ends_with("CORR")) %>%
 distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("STROOP")), as.numeric)
  
Stroop.comp.sum <- d.Stroop.comp %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(Stroop.comp.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "Stroop (Stroop Effect in ms) Summary Table") %>% kable_styling()

#plotting summary of scores across condition
p.Stroop.comp <- ggplot(d.Stroop.comp, aes(STROOP_INCONG_MINUS_CONG_CORR)) +
  geom_histogram() +
  labs(title = "Average Stroop Effect per Subject in BABS Sample") +
  theme_classic()
p.Stroop.comp
```

### NIH Toolbox: Flanker
Note: Raw scores might not be informative since almost everyone has this same raw score.

```{r Flanker, warning=FALSE, message=FALSE}
#creating data frame with relevant variables
d.Flanker <- d.NIH %>% select(BABS_ID, TestName, Key, Value) %>%
 filter(TestName == "Flank_2") %>% filter(Key == "RawScore") %>%
  mutate_at(vars(starts_with("Value")), as.numeric)
  
Flanker.sum <- d.Flanker %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "TestName*") %>% filter(Variable != "Key*")

kable(Flanker.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "NIH Toolbox Flanker (Raw Score) Summary Table") %>% kable_styling()

#plotting summary of scores across condition
p.Flanker <- ggplot(d.Flanker, aes(Value)) +
  geom_histogram() +
  labs(title = "Flanker Raw Scores in BABS Sample") +
  theme_classic()
p.Flanker
```

## Cognitive Flexibility {.tabset}
### NIH Toolbox: Dimensional Change Card Sort (DCCS)

```{r DCCS, warning=FALSE, message=FALSE}
#creating data frame with relevant variables
d.DCCS<- d.NIH %>% select(BABS_ID, TestName, Key, Value) %>%
 filter(TestName == "DCCS_2") %>% filter(Key == "RawScore") %>%
  mutate_at(vars(starts_with("Value")), as.numeric)
  
DCCS.sum <- d.DCCS %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "TestName*") %>% filter(Variable != "Key*")

kable(DCCS.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "NIH Toolbox DCCS (Raw Score) Summary Table") %>% kable_styling()

#plotting summary of scores across condition
p.DCCS <- ggplot(d.DCCS, aes(Value)) +
  geom_histogram() +
  labs(title = "DCCS Raw Scores in BABS Sample") +
  theme_classic()
p.DCCS
```

### Cognitive Reflection Test
Note: Scores can only range from 0-3; BABS_031 has a score of -3.

```{r CogReflect, warning=FALSE, message=FALSE}
d.CRT <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("CRT")) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("CRT")), as.numeric)
#counting the number of observations and summarizing mean & SD
CRT.sum <- d.CRT %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(CRT.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "Cognitive Relfection Summary Table") %>% kable_styling()
#plotting distribution of scores
p.CRT <- ggplot(d.CRT, aes(CRT)) +
  geom_bar() + 
  labs(title = "Cognitive Relfection Scores in BABS Sample") +
  theme_classic()
p.CRT
```

## Learning and Memory {.tabset}
### California Verbal Learning Test (CVLT)

```{r CVLT, warning=FALSE, message=FALSE}
d.CVLT <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("CVLT")) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("CVLT")), as.numeric)
#counting the number of observations and summarizing mean & SD
CVLT.sum <- d.CVLT %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(CVLT.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "CVLT Summary Table") %>% kable_styling()
```

### Face-Name Associative Memory Examination (FNAME)

```{r FNAME, warning=FALSE, message=FALSE}
d.FME <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("FME")) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("FME")), as.numeric)
#counting the number of observations and summarizing mean & SD
FME.sum <- d.FME %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(FME.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "Face-Name Associative Memory Summary Table") %>% kable_styling()
```

## Visuospatial {.tabset}
### Visual Reproduction
Note: Scores for each sub-scale range from 0-104. BABS055 has a VR2 score = 119; verify actual score.

```{r VisRepro, warning=FALSE, message=FALSE}
d.WMS <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("WMS")) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("WMS")), as.numeric)
#counting the number of observations and summarizing mean & SD
WMS.sum <- d.WMS %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(WMS.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "Visual Reproduction Summary Table") %>% kable_styling()
#creating long data frame
d.WMS.long <- d.WMS %>% 
  pivot_longer(names_to = "Facet", values_to = "Score", -c(BABS_ID, `AGE AT SESSION`))
#plotting distribution of scores**
p.WMS <- ggplot(d.WMS.long, aes(Score)) +
  geom_bar() + 
  labs(title = "Visual Recognition Scores in BABS Sample") +
  theme_classic() + facet_grid(.~ Facet)
p.WMS
```

## Fluid Intelligence {.tabset}
### WASI-II Matrix Reasoning

```{r MatrixReason, warning=FALSE, message=FALSE}
d.matrix <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, WASI_MATRIX_SCORE) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("WASI")), as.numeric)
#counting the number of observations and summarizing mean & SD
Matrix.sum <- d.matrix %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(Matrix.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "WASI Matrix Reasoning Summary Table") %>% kable_styling()
#plotting distribution of scores
p.matrix <- ggplot(d.matrix, aes(WASI_MATRIX_SCORE)) +
  geom_bar() + 
  labs(title = "WASI Matrix Reasoning Scores in BABS Sample") +
  theme_classic()
p.matrix
```

## Creativity {.tabset}
### Remote Associates Test

```{r RemoteAssoc, warning=FALSE, message=FALSE}
d.remoteAssoc <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, REMOTE_ASSOCIATES) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
   mutate_at(vars(starts_with("REMOTE")), as.numeric)
#counting the number of observations and summarizing mean & SD
remoteAssoc.sum <- d.remoteAssoc %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(remoteAssoc.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "Remote Associates Summary Table") %>% kable_styling()
#plotting distribution of scores
p.remoteAssoc <- ggplot(d.remoteAssoc, aes(REMOTE_ASSOCIATES)) +
  geom_bar() + 
  labs(title = "Remote Associates Scores in BABS Sample") +
  theme_classic()
p.remoteAssoc
```

## Crystalized Intelligence {.tabset}
### WASI-II Vocab
Note: need to look up the range of acceptable scores to verify values.

```{r WASI_vocab, warning=FALSE, message=FALSE}
#creating data frame with relevant variables
d.vocab <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, WASI_VOCAB_SCORE) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
   mutate_at(vars(starts_with("WASI")), as.numeric)
#counting the number of observations and summarizing mean & SD
Vocab.sum <- d.vocab %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(Matrix.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "WASI Vocab Summary Table") %>% kable_styling()
#plotting distribution of scores
p.vocab <- ggplot(d.vocab, aes(WASI_VOCAB_SCORE)) +
  geom_bar() + 
  labs(title = "WASI Vocab Scores in BABS Sample") +
  theme_classic()
p.vocab
```

### C-Test
Note: Stopped administration after BABS_173. Unknown range of acceptable values.

```{r CTest, warning=FALSE, message=FALSE}
#creating data frame with relevant variables
d.cTest <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, CTEST) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
   mutate_at(vars(starts_with("CTEST")), as.numeric)
#counting the number of observations and summarizing mean & SD
cTest.sum <- d.cTest %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(cTest.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "C-Test Summary Table") %>% kable_styling()
#plotting distribution of scores
p.cTest <- ggplot(d.cTest, aes(CTEST)) +
  geom_bar() + 
  labs(title = "C-Test Scores in BABS Sample") +
  theme_classic()
p.cTest
```

# Individual Difference Questionnaires {.tabset}
## Lifestyle {.tabset}
### Lifetime Experiences Questionnaire (LEQ)
Variable number of responses across items; will need to verify with notes to confirm.

```{r LEQ, warning=FALSE, message=FALSE}
#creating data frame with relevant variables
d.LEQ <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("LEQ")) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("LEQ")), as.numeric) %>%
  mutate(LEQ_YA_total = (LEQ_YA_A + LEQ_YA_B)*1.05 + LEQ_YA_C,
         LEQ_MA_total = (LEQ_MID_A + LEQ_MID_B)*0.25 + LEQ_MID_D + LEQ_MID_C,
         LEQ_OA_total = (LEQ_LATE_A*0.4) + LEQ_LATE_C + LEQ_LATE_B,
         LEQ_total = LEQ_YA_total + LEQ_MA_total + LEQ_OA_total)
#counting the number of observations and summarizing mean & SD
LEQ.sum <- d.LEQ %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION") %>% filter(Variable != "LEQ NOTES")

kable(LEQ.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "LEQ Summary Table") %>% kable_styling()
```

## Depressive and Anxious Traits {.tabset}
### Geriatric Depression Questionnaire (GDS)

```{r GDS, warning=FALSE, message=FALSE}
d.GDS <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, GDS) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("GDS")), as.numeric)
#counting the number of observations and summarizing mean & SD
GDS.sum <- d.GDS %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(GDS.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "GDS Summary Table") %>% kable_styling()
#plotting distribution of scores
p.GDS <- ggplot(d.GDS, aes(GDS)) +
  geom_bar() + 
  labs(title = "GDS Scores in BABS Sample") +
  theme_classic()
p.GDS
```

### Mood and Anxiety Symptom Questionnaire (MASQ-30)

```{r MASQ, warning=FALSE, message=FALSE}
d.MASQ <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("MASQ")) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("MASQ")), as.numeric)
#counting the number of observations and summarizing mean & SD
MASQ.sum <- d.MASQ %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(MASQ.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "MASQ Summary Table") %>% kable_styling()
#creating long data frame
d.MASQ.long <- d.MASQ %>% 
  pivot_longer(names_to = "Facet", values_to = "Score", -c(BABS_ID, `AGE AT SESSION`))
#plotting distribution of scores**
p.MASQ <- ggplot(d.MASQ.long, aes(Score)) +
  geom_bar() + 
  labs(title = "MASQ Scores in BABS Sample") +
  theme_classic() + facet_grid(.~ Facet)
p.MASQ
```

### Penn State Worry Questionnaire

```{r PSWQ, warning=FALSE, message=FALSE}
d.PSWQ <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, PSWQ) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("PSWQ")), as.numeric)
#counting the number of observations and summarizing mean & SD
PSWQ.sum <- d.PSWQ %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(PSWQ.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "Penn State Worry Summary Table") %>% kable_styling()
#plotting distribution of scores
p.PSWQ <- ggplot(d.PSWQ, aes(PSWQ)) +
  geom_bar() + 
  labs(title = "Penn State Worry Scores in BABS Sample") +
  theme_classic()
p.PSWQ
```

## Sleep {.tabset}
### Pittsburgh Sleep Quality Index (PSQI)

```{r PSQI, warning=FALSE, message=FALSE}
d.PSQI <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("PSQI")) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("PSQI")), as.numeric)
#counting the number of observations and summarizing mean & SD
PSQI.sum <- d.PSQI %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(PSQI.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "Pittsburgh Sleep Quality Summary Table") %>% kable_styling()
#creating long data frame
d.PSQI.long <- d.PSQI %>% 
  pivot_longer(names_to = "Facet", values_to = "Score", -c(BABS_ID, `AGE AT SESSION`))
#plotting distribution of scores**
p.PSQI <- ggplot(d.PSQI.long, aes(Score)) +
  geom_bar() + 
  labs(title = "Pittsburgh Sleep Quality Scores in BABS Sample") +
  theme_classic() + facet_wrap(.~ Facet)
p.PSQI
```

## Meta-cognition {.tabset}
### Metamemory Questionnaire for Older Adults

```{r OA_Metamemory, warning=FALSE, message=FALSE}
d.Metamem <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("METAMEMORY")) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("METAMEMORY")), as.numeric)
#counting the number of observations and summarizing mean & SD
Metamem.sum <- d.Metamem %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(Metamem.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "OA Metamemory Summary Table") %>% kable_styling()
#creating long data frame
d.Metamem.long <- d.Metamem %>% 
  pivot_longer(names_to = "Facet", values_to = "Score", -c(BABS_ID, `AGE AT SESSION`))
#plotting distribution of scores
p.metamem <- ggplot(d.Metamem.long, aes(Score)) +
  geom_bar() + 
  labs(title = "Metamemory Scores in BABS Sample") +
  theme_classic() + facet_grid(.~ Facet)
p.metamem

#flagging non-integer values
flag.metamem <- d.Metamem.long %>% mutate(integ_test = is_wholenumber(d.Metamem.long$Score)) %>%
     filter(integ_test == FALSE)
kable(flag.metamem, caption = "Incorrectly entered (non-integer) values for the Metamemory Questionnaire") %>% kable_styling()
```

### Behavior Rating Inventory of Executive Function-Adult (BRIEF-A)

```{r Brief_A, warning=FALSE, message=FALSE}
d.BRIEF <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("BRIEF")) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("BRIEF")), as.numeric)
#counting the number of observations and summarizing mean & SD
BRIEF.sum <- d.BRIEF %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(BRIEF.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "BRIEF-A Summary Table") %>% kable_styling()
#creating long data frame
d.BRIEF.long <- d.BRIEF %>% 
  pivot_longer(names_to = "Facet", values_to = "Score", -c(BABS_ID, `AGE AT SESSION`))
#plotting distribution of scores
p.BRIEF <- ggplot(d.BRIEF.long, aes(Score)) +
  geom_bar() + 
  labs(title = "BRIEF-A Scores in BABS Sample") +
  theme_classic() + facet_wrap(.~ Facet)
p.BRIEF
```

## Motivation {.tabset}
### Selection-Optimization-Compensation Questionnaire (SOCQ)

```{r SOCQ, warning=FALSE, message=FALSE}
d.SOCQ <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("SOCQ")) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("SOCQ")), as.numeric)
#counting the number of observations and summarizing mean & SD
SOCQ.sum <- d.SOCQ %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(SOCQ.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "Seletion-Optimization-Compensation Summary Table") %>% kable_styling()
#creating long data frame
d.SOCQ.long <- d.SOCQ %>% 
  pivot_longer(names_to = "Facet", values_to = "Score", -c(BABS_ID, `AGE AT SESSION`))
#plotting distribution of scores
p.SOCQ <- ggplot(d.SOCQ.long, aes(Score)) +
  geom_bar() + 
  labs(title = "SOC Questionnaire Scores in BABS Sample") +
  theme_classic() + facet_wrap(.~ Facet)
p.SOCQ

#flagging values that are incorrect, given the constraints of the scale
flag.socq <- d.SOCQ.long %>% mutate(integ_test = is_wholenumber(d.SOCQ.long$Score)) %>%
  filter(integ_test == FALSE)
kable(flag.socq, caption = "Incorrectly entered values for the SOCQ") %>% kable_styling()
```

### BIS/BAS

```{r BISBAS, warning=FALSE, message=FALSE}
d.BISBAS <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("BISBAS")) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("BISBAS")), as.numeric)
#counting the number of observations and summarizing mean & SD
BISBAS.sum <- d.BISBAS %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(BISBAS.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "BIS-BAS Summary Table") %>% kable_styling()
#creating long data frame
d.BISBAS.long <- d.BISBAS %>% 
  pivot_longer(names_to = "Facet", values_to = "Score", -c(BABS_ID, `AGE AT SESSION`))
#plotting distribution of scores
p.BISBAS <- ggplot(d.BISBAS.long, aes(Score)) +
  geom_bar() + 
  labs(title = "BIS-BAS Scores in BABS Sample") +
  theme_classic() + facet_grid(.~ Facet)
p.BISBAS
```

### Barratt Impulsiveness Scale (BIS-11)

```{r BIS, warning=FALSE, message=FALSE}
d.BIS <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("BIS_")) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("BIS")), as.numeric)
#counting the number of observations and summarizing mean & SD
BIS.sum <- d.BIS %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(BIS.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "BIS Summary Table") %>% kable_styling()
#creating long data frame
d.BIS.long <- d.BIS %>% 
  pivot_longer(names_to = "Facet", values_to = "Score", -c(BABS_ID, `AGE AT SESSION`))
#plotting distribution of scores
p.BIS <- ggplot(d.BIS.long, aes(Score)) +
  geom_bar() + 
  labs(title = "BIS Scores in BABS Sample") +
  theme_classic() + facet_grid(.~ Facet)
p.BIS
```

### Grit Scale

```{r Grit, warning=FALSE, message=FALSE}
d.Grit <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("GRIT")) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("GRIT")), as.numeric)
#counting the number of observations and summarizing mean & SD
Grit.sum <- d.Grit %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(Grit.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "Grit Summary Table") %>% kable_styling()
#creating long data frame
d.Grit.long <- d.Grit %>% 
  pivot_longer(names_to = "Facet", values_to = "Score", -c(BABS_ID, `AGE AT SESSION`))
#plotting distribution of scores
p.Grit <- ggplot(d.Grit.long, aes(Score)) +
  geom_bar() + 
  labs(title = "Grit Questionnaire Scores in BABS Sample") +
  theme_classic() + facet_wrap(.~ Facet)
p.Grit
```

### Zimbardo Time Perspective Scale

```{r ZTPS, warning=FALSE, message=FALSE}
d.ZTP <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("ZTP")) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("ZTP")), as.numeric)
#counting the number of observations and summarizing mean & SD
ZTP.sum <- d.ZTP %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "AGE AT SESSION")

kable(ZTP.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "Zimbardo Time Perspective Summary Table") %>% kable_styling()
```
