---
title: "BABS Working Memory Summary"
author: "JLC"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---

# Working Memory Measures: BABS Neuropsych Battery

```{r setup, warning=FALSE, message=FALSE}
rm(list=ls())

# Packages
library(knitr); library(kableExtra); library(RColorBrewer); library(correlation); library(see); library(readxl); library(psych); library(tidyverse)

#Create data directories
NP.path<-"/Volumes/berry-lab/berry-lab/Brandeis_Aging_Brain_Study/BABS Data/Analysis/BABS NP MASTER.xlsx"
sess.path <-"/Volumes/berry-lab/berry-lab/Brandeis_Aging_Brain_Study/BABS Data/"

#Make data frames for neuropsych battery items from excel spreadsheet
BABS.NP.sess1 <- read_xlsx(NP.path, sheet = "Session 1")
```

## Digit Span
### Forward
Variable name: DS_For = Digit Span Forward Score

```{r DigSpan_for, warning=FALSE, message=FALSE}
#creating data frame with relevant variables
d.DigSpan.F <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, DIGITSPAN_FORWARD) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
    mutate_at(vars(starts_with("DIGITSPAN")), as.numeric)
```

### Backward
Variable name: DS_Back = Digit Span Backward Score

```{r DigSpan_back, warning=FALSE, message=FALSE}
#creating data frame with relevant variables
d.DigSpan.B <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, DIGITSPAN_BACKWARD) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(starts_with("DIGITSPAN")), as.numeric)
```

## Keep Track Task
#### Early participants BABS001-BABS024 underwent "easier" version of the Keep Track; these data are analyzed separately
Variable names: KT_2 = Two Categories; KT_3 = Three Categories; KT_4 = Four Categories

```{r KeepTrack, warning=FALSE, message=FALSE}
#creating data frame with relevant variables
d.KeepTrack <- BABS.NP.sess1 %>% select(BABS_ID, `AGE AT SESSION`, starts_with("KEEP"), THREECATEGORIES_TOTAL) %>%
                                          distinct(BABS_ID, .keep_all = T) %>%
  mutate_at(vars(ends_with("TOTAL")), as.numeric)
```

## Spatial N-Back
#### Early participants BABS001-BABS024 underwent "easier" version of the N-Back; these data are analyzed separately
Variable names: NBack_ACC_1 = 1-Back Accuracy; NBack_ACC_2 = 2-Back Accuracy; NBack_RT_1 = 1-Back RT; NBack_RT_2 = 2-Back RT

```{r Nback_datawrangle, warning=FALSE, message=FALSE}
#Make data frames for N-Back data
#Early participants BABS001-BABS024 underwent "easier" version of the N-Back
#"Easy" Conditions from Session 1
sub.IDs.sess1.easy <- c("BABS005", "BABS006","BABS008", "BABS024")
sub.IDs.sess1.easy.num.tb <- sub.IDs.sess1.easy %>% as_tibble() %>%
  mutate(num.var = str_remove(value, "^BABS")) %>% select(num.var)
sub.IDs.sess1.easy.num <- as.character(sub.IDs.sess1.easy.num.tb$num.var)
#data frame
Nback.easy.sess1 <- data_frame()
  for (nid in 1:length(sub.IDs.sess1.easy.num)) { 
      Nback.fname <- paste0(sess.path, "BABS", sub.IDs.sess1.easy.num[nid], "/Session_1/NBACK/","N-Back_", sub.IDs.sess1.easy.num[nid], "-1.xlsx");
      file_data <- read_xlsx(Nback.fname, skip=1) %>% select(Subject, blockListOneBack, blockListTwoBack, Trial, `image[Trial]`, `stim.ACC[Trial]`,  `stim.RT[Trial]`);
Nback.easy.sess1 <- bind_rows(Nback.easy.sess1, file_data);
  }
#creating tidy data frame
Nback.easy.sess1.clean <- Nback.easy.sess1 %>% filter(Trial <25) %>%
  mutate(Level = if_else(blockListOneBack < 4 & !is.na(blockListOneBack), 1, 2),
         Block = if_else(blockListOneBack < 4  & !is.na(blockListOneBack), blockListOneBack, blockListTwoBack), 
         ACC = `stim.ACC[Trial]`,
         RT = `stim.RT[Trial]`) %>%
  select(Subject, Level, Block, Trial, ACC, RT)
#"Easy" Conditions from Session 2
sub.IDs.sess2.easy <- c("BABS004", "BABS007", "BABS009", "BABS010", "BABS011", "BABS012", "BABS013", "BABS014", "BABS015", "BABS016", "BABS017", "BABS019", "BABS020", "BABS021", "BABS022", "BABS023")
sub.IDs.sess2.easy.num.tb <- sub.IDs.sess2.easy %>% as_tibble() %>%
  mutate(num.var = str_remove(value, "^BABS")) %>% select(num.var)
sub.IDs.sess2.easy.num <- as.character(sub.IDs.sess2.easy.num.tb$num.var)
#data frame
Nback.easy.sess2 <- data_frame()
  for (nid in 1:length(sub.IDs.sess2.easy.num)) { 
      Nback.fname <- paste0(sess.path, "BABS", sub.IDs.sess2.easy.num[nid], "/Session_2/NBACK/","N-Back_", sub.IDs.sess2.easy.num[nid], "-2.xlsx");
      file_data <- read_xlsx(Nback.fname, skip=1) %>% select(Subject, blockListOneBack, blockListTwoBack, Trial, `image[Trial]`, `stim.ACC[Trial]`,  `stim.RT[Trial]`);
Nback.easy.sess2 <- bind_rows(Nback.easy.sess2, file_data);
  }
#creating tidy data frame
Nback.easy.sess2.clean <- Nback.easy.sess2 %>% filter(Trial <25) %>%
  mutate(Level = if_else(blockListOneBack < 4 & !is.na(blockListOneBack), 1, 2),
         Block = if_else(blockListOneBack < 4  & !is.na(blockListOneBack), blockListOneBack, blockListTwoBack), 
         ACC = `stim.ACC[Trial]`,
         RT = `stim.RT[Trial]`) %>%
  select(Subject, Level, Block, Trial, ACC, RT)
#creating merged data frame with all "easy" subjects
d.Nback.easy <- rbind(Nback.easy.sess1.clean, Nback.easy.sess2.clean)
#"Hard" Conditions from Session 2 
sub.IDs.sess2.hard <- c("BABS025","BABS026","BABS028","BABS029","BABS030","BABS031","BABS033","BABS035","BABS036","BABS037","BABS038","BABS040", "BABS042")
sub.IDs.sess2.hard.num.tb <- sub.IDs.sess2.hard %>% as_tibble() %>%
  mutate(num.var = str_remove(value, "^BABS")) %>% select(num.var)
sub.IDs.sess2.hard.num <- as.character(sub.IDs.sess2.hard.num.tb$num.var)
#data frame
Nback.hard.sess2 <- data_frame()
  for (nid in 1:length(sub.IDs.sess2.hard.num)) { 
      Nback.fname <- paste0(sess.path, "BABS", sub.IDs.sess2.hard.num[nid], "/Session_2/NBACK/","N-Back_", sub.IDs.sess2.hard.num[nid], "-2.xlsx");
      file_data <- read_xlsx(Nback.fname, skip=1) %>% select(Subject, blockListOneBack, blockListTwoBack, Trial, `image[Trial]`, `stim.ACC[Trial]`,  `stim.RT[Trial]`);
Nback.hard.sess2 <- bind_rows(Nback.hard.sess2, file_data);
  }
#creating tidy data frame
Nback.hard.sess2.clean <- Nback.hard.sess2 %>% filter(Trial <25) %>%
  mutate(Level = if_else(blockListOneBack < 4 & !is.na(blockListOneBack), 1, 2),
         Block = if_else(blockListOneBack < 4  & !is.na(blockListOneBack), blockListOneBack, blockListTwoBack), 
         ACC = `stim.ACC[Trial]`,
         RT = `stim.RT[Trial]`) %>%
  select(Subject, Level, Block, Trial, ACC, RT)
#"Hard" Conditions from Session 1 (BABS 273 needs to be converted; 286, 288 have corrupted files)
sub.IDs.sess1.hard.1 <- c("BABS043", "BABS044", "BABS045", "BABS046", "BABS049", "BABS051", "BABS053", "BABS055", "BABS056", "BABS057", "BABS058", "BABS059", "BABS060", "BABS061", "BABS062", "BABS066", "BABS067", "BABS069", "BABS070", "BABS071", "BABS072", "BABS073", "BABS074", "BABS075", "BABS076", "BABS077", "BABS079", "BABS080", "BABS081", "BABS082", "BABS083", "BABS084", "BABS085", "BABS086", "BABS087", "BABS088", "BABS089", "BABS090", "BABS091", "BABS092", "BABS093", "BABS094", "BABS095", "BABS096", "BABS097", "BABS098", "BABS099", "BABS100", "BABS101", "BABS102", "BABS104", "BABS105")

sub.IDs.sess1.hard.2 <- c("BABS106", "BABS107", "BABS108", "BABS110", "BABS111", "BABS112", "BABS113", "BABS114", "BABS115", "BABS116", "BABS117", "BABS118", "BABS119", "BABS121", "BABS122", "BABS124", "BABS125", "BABS126", "BABS128", "BABS129", "BABS130", "BABS131", "BABS132", "BABS133", "BABS134", "BABS135", "BABS136", "BABS138", "BABS139", "BABS141", "BABS142", "BABS143", "BABS145", "BABS146", "BABS147", "BABS148", "BABS150", "BABS151", "BABS152", "BABS154", "BABS155", "BABS157", "BABS158", "BABS159", "BABS160", "BABS161", "BABS162", "BABS163", "BABS166", "BABS168", "BABS169", "BABS170", "BABS171", "BABS172", "BABS173", "BABS174", "BABS175", "BABS176", "BABS177", "BABS179", "BABS180", "BABS181", "BABS196", "BABS266", "BABS272", "BABS279", "BABS284")
#for sheets without header line deleted
sub.IDs.sess1.hard.num.tb.1 <- sub.IDs.sess1.hard.1 %>% as_tibble() %>%
  mutate(num.var = str_remove(value, "^BABS")) %>% select(num.var)
sub.IDs.sess1.hard.num.1 <- as.character(sub.IDs.sess1.hard.num.tb.1$num.var)
#data frame
Nback.hard.sess1 <- data_frame()
  for (nid in 1:length(sub.IDs.sess1.hard.num.1)) { 
      Nback.fname <- paste0(sess.path, "BABS", sub.IDs.sess1.hard.num.1[nid], "/Session_1/NBACK/","N-Back_", sub.IDs.sess1.hard.num.1[nid], "-1.xlsx");
      file_data <- read_xlsx(Nback.fname, skip=1) %>% select(Subject, blockListOneBack, blockListTwoBack, Trial, `image[Trial]`, `stim.ACC[Trial]`,  `stim.RT[Trial]`);
Nback.hard.sess1 <- bind_rows(Nback.hard.sess1, file_data);
  }
#for sheets with header line deleted
sub.IDs.sess1.hard.num.tb.2 <- sub.IDs.sess1.hard.2 %>% as_tibble() %>%
  mutate(num.var = str_remove(value, "^BABS")) %>% select(num.var)
sub.IDs.sess1.hard.num.2 <- as.character(sub.IDs.sess1.hard.num.tb.2$num.var)
#data frame
Nback.hard.sess1.2 <- data_frame()
  for (nid in 1:length(sub.IDs.sess1.hard.num.2)) { 
      Nback.fname <- paste0(sess.path, "BABS", sub.IDs.sess1.hard.num.2[nid], "/Session_1/NBACK/","N-Back_", sub.IDs.sess1.hard.num.2[nid], "-1.xlsx");
      file_data <- read_xlsx(Nback.fname) %>% select(Subject, blockListOneBack, blockListTwoBack, Trial, `image[Trial]`, `stim.ACC[Trial]`,  `stim.RT[Trial]`);
Nback.hard.sess1.2 <- bind_rows(Nback.hard.sess1.2, file_data);
  }
#creating tidy data frames
Nback.hard.sess2.clean.1 <- Nback.hard.sess1 %>% filter(Trial <25) %>%
  mutate(Level = if_else(blockListOneBack < 4 & !is.na(blockListOneBack), 1, 2),
         Block = if_else(blockListOneBack < 4  & !is.na(blockListOneBack), blockListOneBack, blockListTwoBack), 
         ACC = `stim.ACC[Trial]`,
         RT = `stim.RT[Trial]`) %>%
  select(Subject, Level, Block, Trial, ACC, RT)
Nback.hard.sess2.clean.2 <- Nback.hard.sess1.2 %>% filter(Trial <25) %>%
  mutate(Level = if_else(blockListOneBack < 4 & !is.na(blockListOneBack), 1, 2),
         Block = if_else(blockListOneBack < 4  & !is.na(blockListOneBack), blockListOneBack, blockListTwoBack), 
         ACC = `stim.ACC[Trial]`,
         RT = `stim.RT[Trial]`) %>%
  select(Subject, Level, Block, Trial, ACC, RT)
#creating merged data frame with all "hard" subjects
d.Nback.hard <- rbind(Nback.hard.sess2.clean, Nback.hard.sess2.clean.1, Nback.hard.sess2.clean.2)
```

```{r NBack, warning=FALSE, message=FALSE}
#summarizing "easy" participants by load level and block
##ACC
Easy.NBack.ACC.sum <- d.Nback.easy %>% select(Level, Block, ACC) %>% group_by(Level, Block) %>% 
  summarise_each(funs(mean,sd,se=sd(.)/sqrt(n())))
##RT
Easy.NBack.RT.sum <- d.Nback.easy %>% select(Level, Block, RT) %>% group_by(Level, Block) %>% filter(RT != 0) %>%
  summarise_each(funs(mean,sd,se=sd(.)/sqrt(n())))

#plotting N-Back performance for "easy" version
p.Nback.easy.acc <- ggplot(Easy.NBack.ACC.sum, aes(x=Block, y=mean)) +
  geom_bar(stat="identity", position=position_dodge(), alpha=.45, size=1.5) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=mean-se, ymax=mean+se), width=.2, size=1.25) +  
  labs(title = "N-Back (Easy Version) Scores in BABS Sample") +
  theme_classic() + facet_grid(.~Level)
p.Nback.easy.acc
p.Nback.easy.RT <- ggplot(Easy.NBack.RT.sum, aes(x=Block, y=mean)) +
  geom_bar(stat="identity", position=position_dodge(), alpha=.45, size=1.5) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=mean-se, ymax=mean+se), width=.2, size=1.25) +  
  labs(title = "N-Back (Easy Version) RT in BABS Sample") +
  theme_classic() + facet_grid(.~Level)
p.Nback.easy.RT

#summarizing "hard" participants by load level and block
##ACC
Hard.NBack.ACC.sum <- d.Nback.hard %>% select(Level, Block, ACC) %>% group_by(Level, Block) %>% 
  summarise_each(funs(mean,sd,se=sd(.)/sqrt(n())))
##RT
Hard.NBack.RT.sum <- d.Nback.hard %>% select(Level, Block, RT) %>% group_by(Level, Block) %>% filter(RT != 0) %>%
  summarise_each(funs(mean,sd,se=sd(.)/sqrt(n())))

#plotting N-Back performance for "hard" version (133 participants with both levels of N)
p.Nback.hard.acc <- ggplot(Hard.NBack.ACC.sum, aes(x=Block, y=mean)) +
  geom_bar(stat="identity", position=position_dodge(), alpha=.45, size=1.5) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=mean-se, ymax=mean+se), width=.2, size=1.25) +  
  labs(title = "N-Back (Hard Version) Scores in BABS Sample") +
  theme_classic() + facet_grid(.~Level)
p.Nback.hard.acc
p.Nback.hard.RT <- ggplot(Hard.NBack.RT.sum, aes(x=Block, y=mean)) +
  geom_bar(stat="identity", position=position_dodge(), alpha=.45, size=1.5) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=mean-se, ymax=mean+se), width=.2, size=1.25) +  
  labs(title = "N-Back (Hard Version) RT in BABS Sample") +
  theme_classic() + facet_grid(.~Level)
p.Nback.hard.RT

#summarizing ACC across load levels
Hard.NBack.ACC.agg.sum <- d.Nback.hard %>% select(Level, ACC) %>% group_by(Level) %>% 
  summarise_each(funs(mean,sd,se=sd(.)/sqrt(n())))

Hard.NBack.ACC.subj.sum <- d.Nback.hard %>% select(Subject, Level, ACC) %>% group_by(Subject, Level) %>% 
  summarise_each(funs(mean,sd,se=sd(.)/sqrt(n())))
#plot
Hard.NBack.ACC.agg.sum$Level <- factor(Hard.NBack.ACC.agg.sum$Level, levels = c(1,2), labels = c(1,2))
fig.Nback.lines <- ggplot(Hard.NBack.ACC.agg.sum, aes(x=Level, y=mean)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), axis.title.y = element_text(face="bold", size=16),legend.title = element_text(face="bold", size=16)) +
  geom_bar(stat="identity", position=position_dodge(), alpha=.45, size=1.5) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=mean-se, ymax=mean+se), width=.2, size=1.25) +  
  geom_point(data = Hard.NBack.ACC.subj.sum, aes(x=Level, y=mean),
             stat="identity", alpha=0.7) +
  geom_line(data = Hard.NBack.ACC.subj.sum, aes(x=Level, y=mean, group=Subject, colour = factor(Subject)), alpha = .5) +
  xlab("N-Back Level") + ylab("Percent Correct")
fig.Nback <- fig.Nback.lines + guides(colour=FALSE)
fig.Nback

#summarizing RT across load levels
Hard.NBack.RT.agg.sum <- d.Nback.hard %>% select(Level, RT) %>% group_by(Level) %>% filter(RT != 0) %>%
  summarise_each(funs(mean,sd,se=sd(.)/sqrt(n())))

Hard.NBack.RT.subj.sum <- d.Nback.hard %>% select(Subject, Level, RT) %>% group_by(Subject, Level) %>% filter(RT != 0) %>% summarise_each(funs(mean,sd,se=sd(.)/sqrt(n())))
#plot
Hard.NBack.RT.agg.sum$Level <- factor(Hard.NBack.RT.agg.sum$Level, levels = c(1,2), labels = c(1,2))
fig.Nback.lines.RT <- ggplot(Hard.NBack.RT.agg.sum, aes(x=Level, y=mean)) + 
  theme(plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"), axis.title.y = element_text(face="bold", size=16),legend.title = element_text(face="bold", size=16)) +
  geom_bar(stat="identity", position=position_dodge(), alpha=.45, size=1.5) +
  geom_errorbar(position=position_dodge(width=0.9), aes(ymin=mean-se, ymax=mean+se), width=.2, size=1.25) +  
  geom_point(data = Hard.NBack.RT.subj.sum, aes(x=Level, y=mean),
             stat="identity", alpha=0.7) +
  geom_line(data = Hard.NBack.RT.subj.sum, aes(x=Level, y=mean, group=Subject, colour = factor(Subject)), alpha = .5) +
  xlab("N-Back Level") + ylab("RT")
fig.Nback.RT <- fig.Nback.lines.RT + guides(colour=FALSE)
fig.Nback.RT
```

## Examining the correlational structure of the working memory tasks (for "Hard" Task subjects only)

```{r corr, warning=FALSE, message=FALSE}
#BABS subject IDs for analysis
sub.IDs <- c("BABS025","BABS026","BABS028","BABS029","BABS030","BABS031","BABS033","BABS035","BABS036","BABS037","BABS038","BABS040", "BABS042", "BABS043", "BABS044", "BABS045", "BABS046", "BABS049", "BABS051", "BABS053", "BABS055", "BABS056", "BABS057", "BABS058", "BABS059", "BABS060", "BABS061", "BABS062", "BABS066", "BABS067", "BABS069", "BABS070", "BABS071", "BABS072", "BABS073", "BABS074", "BABS075", "BABS076", "BABS077", "BABS079", "BABS080", "BABS081", "BABS082", "BABS083", "BABS084", "BABS085", "BABS086", "BABS087", "BABS088", "BABS089", "BABS090", "BABS091", "BABS092", "BABS093", "BABS094", "BABS095", "BABS096", "BABS097", "BABS098", "BABS099", "BABS100", "BABS101", "BABS102", "BABS104", "BABS105", "BABS106", "BABS107", "BABS108", "BABS110", "BABS111", "BABS112", "BABS113", "BABS114", "BABS115", "BABS116", "BABS117", "BABS118", "BABS119", "BABS121", "BABS122", "BABS124", "BABS125", "BABS126", "BABS128", "BABS129", "BABS130", "BABS131", "BABS132", "BABS133", "BABS134", "BABS135", "BABS136", "BABS138", "BABS139", "BABS141", "BABS142", "BABS143", "BABS145", "BABS146", "BABS147", "BABS148", "BABS150", "BABS151", "BABS152", "BABS154", "BABS155", "BABS157", "BABS158", "BABS159", "BABS160", "BABS161", "BABS162", "BABS163", "BABS166", "BABS168", "BABS169", "BABS170", "BABS171", "BABS172", "BABS173", "BABS174", "BABS175", "BABS176", "BABS177", "BABS179", "BABS180", "BABS181", "BABS196", "BABS266", "BABS272", "BABS279", "BABS284")
#merging data frames and cleaning data
d.DigSpan.F.trim <- d.DigSpan.F %>% filter(BABS_ID %in% sub.IDs) %>% mutate(Subject = parse_number(BABS_ID)) %>% select(-BABS_ID)
d.DigSpan.B.trim <- d.DigSpan.B %>% filter(BABS_ID %in% sub.IDs) %>% select(BABS_ID, DIGITSPAN_BACKWARD) %>% mutate(Subject = parse_number(BABS_ID)) %>% select(-BABS_ID)
d.digSpan.Trim <- d.DigSpan.F.trim %>% inner_join(d.DigSpan.B.trim)
d.KeepTrack.trim <- d.KeepTrack %>% filter(BABS_ID %in% sub.IDs) %>% select(BABS_ID, KEEPTRACK_TWOCATEGORIES_TOTAL, THREECATEGORIES_TOTAL, KEEPTRACK_FOURCATEGORIES_TOTAL) %>% mutate(Subject = parse_number(BABS_ID)) %>% select(-BABS_ID)
d.NBack.RT.wide<- Hard.NBack.RT.subj.sum %>% select(Subject, mean, Level) %>% pivot_wider(id_cols = Subject, names_from = Level,names_prefix = "NBack_RT_", values_from = mean)
d.NBack.ACC.wide<- Hard.NBack.ACC.subj.sum %>% select(Subject, mean, Level) %>% pivot_wider(id_cols = Subject, names_from = Level,names_prefix = "NBACK_ACC_", values_from = mean)
d.NBack.Trim <-d.NBack.ACC.wide %>% inner_join(d.NBack.RT.wide)
#creating data frame with all WM measures
d.WM <- d.digSpan.Trim %>% inner_join(d.NBack.Trim) %>% inner_join(d.KeepTrack.trim) %>% select(-Subject) %>%
  rename(DS_For = DIGITSPAN_FORWARD, DS_Back = DIGITSPAN_BACKWARD, KT_2 = KEEPTRACK_TWOCATEGORIES_TOTAL, KT_3 = THREECATEGORIES_TOTAL, KT_4 = KEEPTRACK_FOURCATEGORIES_TOTAL)
corr.WM <- correlation(d.WM)
corr.WM %>%
  summary(redundant = F) %>%
  plot() + ggplot2::theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1))
```