---
title: "BABS Neuropsych Summary"
author: "JLC"
date: "`r Sys.Date()`"
output: html_document
---
# Brandeis Aging Brain Study (BABS) Neuropsych Battery: Descriptive Summary

```{r setup, warning=FALSE, message=FALSE}
rm(list=ls())

# Packages
library(lme4); library(knitr); library(kableExtra); library(RColorBrewer); library(correlation); library(tidyverse)

#Create data directories
NP.path<-"/Volumes/berry-lab/berry-lab/Brandeis_Aging_Brain_Study/BABS Data/Analysis/BABS NP MASTER.xlsx"

#Make data frames for Cog-ED, demographics info, and post-task questionnaire
BABS.NP.demo <- read_xlsx(NP.path, sheet = "Demographics")
BABS.NP.sess1 <- read_xlsx(NP.path, sheet = "Session 1")
BABS.NP.sess2 <- read_xlsx(NP.path, sheet = "Session 2")
```

# Behavioral Measures
## General Cognitive Function

### MMSE

```{r MMSE, warning=FALSE, message=FALSE}




```

## Working Memory
### Digit Span
#### Forward

```{r DigSpan_for, warning=FALSE, message=FALSE}




```

#### Backward

```{r DigSpan_back, warning=FALSE, message=FALSE}




```

### Keep Track Task

```{r KeepTrack, warning=FALSE, message=FALSE}




```

### Spatial N-Back

```{r NBack, warning=FALSE, message=FALSE}




```

## Inhibition
### Stroop (Paper version)

```{r Stroop_paper, warning=FALSE, message=FALSE}




```

### Stroop (Computer version)

```{r Stroop_comp, warning=FALSE, message=FALSE}




```

### NIH Toolbox: Flanker

```{r Flanker, warning=FALSE, message=FALSE}




```

## Cognitive Flexibility
### NIH Toolbox: Dimensional Change Card Sort (DCCS)

```{r DCCS, warning=FALSE, message=FALSE}




```

### Cognitive Reflection Test

```{r CogReflect, warning=FALSE, message=FALSE}




```

## Learning and Memory
### California Verbal Learning Test (CVLT)

```{r CVLT, warning=FALSE, message=FALSE}




```

### Face-Name Associative Memory Examination (FNAME)

```{r FNAME, warning=FALSE, message=FALSE}




```

## Visuospatial
### Visual Reproduction

```{r VisRepro, warning=FALSE, message=FALSE}




```

## Fluid Intelligence
### WASI-II Matrix Reasoning

```{r MatrixReason, warning=FALSE, message=FALSE}




```

## Creativity
### Remote Associates Test

```{r RemoteAssoc, warning=FALSE, message=FALSE}




```

### Alternative Uses Task

```{r AltUse, warning=FALSE, message=FALSE}




```

## Crystalized Intelligence
### WASI-II Vocab

```{r WASI_vocab, warning=FALSE, message=FALSE}




```

### C-Test

```{r CTest, warning=FALSE, message=FALSE}




```

# Individual Difference Questionnaires
## Lifestyle
### Lifetime Experiences Questionnaire (LEQ)

```{r LEQ, warning=FALSE, message=FALSE}




```

### BABS Physical Activities Questionnaire

```{r PhysActivity, warning=FALSE, message=FALSE}




```

## Depressive and Anxious Traits
### Geriatric Depression Questionnaire (GDS)

```{r GDS, warning=FALSE, message=FALSE}




```

### Mood and Anxiety Symptom Questionnaire (MASQ-30)

```{r MASQ, warning=FALSE, message=FALSE}




```

### Penn State Worry Questionnaire

```{r PSWQ, warning=FALSE, message=FALSE}




```

## Sleep
### Pittsburgh Sleep Quality Index (PSQI)

```{r PSQI, warning=FALSE, message=FALSE}




```

### Berkeley Retrospective Sleep Questionnaire (BRSQ)

```{r BRSQ, warning=FALSE, message=FALSE}




```

## Meta-cognition
### Multifactorial Memory Questionnaire

```{r MMQ, warning=FALSE, message=FALSE}




```

### Metamemory Questionnaire for Older Adults

```{r OA_Metamemory, warning=FALSE, message=FALSE}




```

### Behavior Rating Inventory of Executive Function-Adult (BRIEF-A)

```{r Brief_A, warning=FALSE, message=FALSE}




```

## Motivation
### Selection-Optimization-Compensation Questionnaire (SOCQ)

```{r SOCQ, warning=FALSE, message=FALSE}




```

### BIS/BAS

```{r BISBAS, warning=FALSE, message=FALSE}




```

### Barratt Impulsiveness Scale (BIS-11)

```{r BIS, warning=FALSE, message=FALSE}




```

### Grit Scale

```{r Grit, warning=FALSE, message=FALSE}




```

### Zimbardo Time Perspective Scale

```{r ZTPS, warning=FALSE, message=FALSE}




```

## Misc
### UCSF Early Developmental History Form

```{r UCSF_Dev, warning=FALSE, message=FALSE}




```