---
title: "BABS BIS Summary"
author: "JLC"
date: "`r Sys.Date()`"
output: 
html_document:
---

# BIS Summary (from BABS Qualtrics data entry)

```{r setup, warning=FALSE, message=FALSE}
rm(list=ls())
#Import relevant packages
library(tidyverse)

# Import data (will update path to Shared Drive once data entry is complete)
BIS.path <- "~/Library/CloudStorage/Box-Box/BABS_Neuropsych/Data/BIS.csv"
BIS <-read.csv(BIS.path, header = T) %>% select(BABS_ID, starts_with("BIS")) %>%
  group_by(BABS_ID) %>% mutate_if(is.character, as.integer) %>% ungroup()
BIS.output.path <- "~/Library/CloudStorage/Box-Box/BABS_Neuropsych/Data/BIS_imputed_sum.csv"
```

## Optional: Participant IDs for summarization

```{r Sub_IDs, warning=FALSE, message=FALSE}
# Enter all participants that you would like to summarize here)
## This section can be commented out if you want to run all available participants
sub.IDs<- c("BABS005", "BABS006","BABS008", "BABS024", "BABS004", "BABS007", "BABS009", "BABS010", "BABS011", "BABS012",
            "BABS013", "BABS014", "BABS015", "BABS016", "BABS017", "BABS019", "BABS020", "BABS021", "BABS022", "BABS023",
            "BABS025","BABS026","BABS028","BABS029","BABS030","BABS031","BABS033","BABS035","BABS036","BABS037","BABS038",
            "BABS040", "BABS042", "BABS043", "BABS044", "BABS045", "BABS046", "BABS049", "BABS051", "BABS053", "BABS055",
            "BABS056", "BABS057", "BABS058", "BABS059", "BABS060", "BABS061", "BABS062", "BABS066", "BABS067", "BABS069",
            "BABS070", "BABS071", "BABS072", "BABS073", "BABS074", "BABS075", "BABS076", "BABS077", "BABS079", "BABS080",
            "BABS081", "BABS082", "BABS083", "BABS084", "BABS085", "BABS086", "BABS087", "BABS088", "BABS089", "BABS090",
            "BABS091", "BABS092", "BABS093", "BABS094", "BABS095", "BABS096", "BABS097", "BABS098", "BABS099", "BABS100",
            "BABS101", "BABS102", "BABS104", "BABS105", "BABS106", "BABS107", "BABS108", "BABS110", "BABS111", "BABS112",
            "BABS113", "BABS114", "BABS115", "BABS116", "BABS117", "BABS118", "BABS119", "BABS121", "BABS122", "BABS124",
            "BABS125", "BABS126", "BABS128", "BABS129", "BABS130", "BABS131", "BABS132", "BABS133", "BABS134", "BABS135",
            "BABS136", "BABS138", "BABS139", "BABS141", "BABS142", "BABS143", "BABS145", "BABS146", "BABS147", "BABS148",
            "BABS150", "BABS151", "BABS152", "BABS154", "BABS155", "BABS157","BABS158", "BABS159", "BABS160", "BABS161",
            "BABS162", "BABS163", "BABS166", "BABS168", "BABS169", "BABS170", "BABS171", "BABS172", "BABS173", "BABS174",
            "BABS175", "BABS176", "BABS177", "BABS179", "BABS180", "BABS181", "BABS196", "BABS266", "BABS272", "BABS279",
            "BABS284")
```

## Cleaning data frame for summary

```{r BIS_clean, warning=FALSE, message=FALSE}
#Creating clean data frame for summary
BIS.clean <- BIS %>% pivot_longer(names_to = "facet", values_to = "response", -c(BABS_ID, BIS_Session)) %>%
  separate_wider_delim(facet,"__", names = c("Scale", "Subscale")) %>%
  separate_wider_delim(Scale,"_", names = c(NA, "Scale")) %>%
  separate_wider_delim(Subscale,".", names = c("Subscale", "Reverse"), too_few = "align_start") %>%
  mutate(reverse_coding = if_else(is.na(Reverse), 0, 1),
         Value = if_else(reverse_coding == 0, response, recode(response, "1" = 4, "2" = 3, "3" = 2, 
                          "4" = 1)),
         Subscale = gsub("[[:digit:]]", "", Subscale)) %>%
  select(BABS_ID, BIS_Session, Scale, Subscale, Value)

#If you would like to create a summary using only a unique subset of participant IDs that you have supplied (in previous code chunk), you can simply add the following line of code to filter the raw data to the code above
# %>% filter(BABS_ID %in% sub.IDs)
```

## Counting the number of missing responses & imputing missing data
### Participants missing > 20% of their data for a given scale will be removed (threshold can be edited for your own purposes)

```{r BIS_impute, warning=FALSE, message=FALSE}
#creating data frame that summarizes the amount of missing data per (sub)scale for each participant
BIS.missing.sum <- BIS.clean %>% group_by(BABS_ID, BIS_Session, Scale) %>%
  summarise(count.missing = sum(is.na(Value)),
            count.response = sum(!is.na(Value))) %>%
  mutate(total = count.missing + count.response,
         prop.missing = count.missing/total,
         flag.missing = if_else(prop.missing > 0.2, 1, 0)) %>%
  filter(flag.missing == 0)
#printing table with the missing data summary
Kable(BIS.missing.sum)
#creating data frame with *only* participants who have accectable amounts of missing data (i.e., < 20% missing)
BIS.clean.IDs <- BIS.missing.sum %>% ungroup() %>% select(BABS_ID, BIS_Session) %>% group_by(BABS_ID, BIS_Session) %>% distinct()
#New data frame with imputed data (using median of the subscale values)
BIS.clean.imputed <- inner_join(BIS.clean, BIS.clean.IDs) %>% group_by(BABS_ID, BIS_Session, Scale, Subscale) %>%
  mutate(median_subscale = round(median(Value, na.rm = T), digits = 0),
         Imputed.Value = if_else(is.na(Value), median_subscale, Value)) %>% ungroup() %>%
  select(BABS_ID, BIS_Session, Scale, Subscale, Imputed.Value)
```

## Creating BIS-Specific Summary Scores with Imputed Values
### First-Order Variables (see data dictionary for details)

```{r BIS_firstOrder, warning=FALSE, message=FALSE}
#data frame with only the first-order summary items
BIS.subscale.sum <- BIS.clean.imputed %>% group_by(BABS_ID, BIS_Session, Subscale) %>%
  summarise(Score = sum(Imputed.Value)) %>%
  pivot_wider(id_cols = c("BABS_ID", "BIS_Session"), names_from = "Subscale", names_prefix = "FirstOrder_", values_from = "Score")
```

### Second-Order Variables

```{r BIS_secondOrder, warning=FALSE, message=FALSE}
#data frame with only the second-order summary items
BIS.scale.sum <- BIS.clean.imputed %>% group_by(BABS_ID, BIS_Session, Scale) %>%
  summarise(Score = sum(Imputed.Value)) %>%
  pivot_wider(id_cols = c("BABS_ID", "BIS_Session"), names_from = "Scale", names_prefix = "SecondOrder_", values_from = "Score")
```

### Combined Summary File

```{r BIS_secondOrder, warning=FALSE, message=FALSE}
#data frame with both the first- and second-order summary items
BIS.sum <- inner_join(BIS.scale.sum, BIS.subscale.sum, by = c("BABS_ID", "BIS_Session"))
#to save the results, un-comment the line below; file path & name can be adjusted in the first code chunk
#write.csv(BIS.sum, file = BIS.output.path, row.names = F)
```