---
title: "BABS MASQ Summary"
author: "JLC"
date: "`r Sys.Date()`"
output: "html_document"
---

# MASQ Summary (from BABS Qualtrics data entry)

```{r setup, warning=FALSE, message=FALSE}
rm(list=ls())
#Import relevant packages
library(kableExtra); library(psych); library(tidyverse)

# Import data
MASQ.path <- "/Volumes/berry-lab/berry-lab/Brandeis_Aging_Brain_Study/BABS Data/Analysis/Qualtrics_Surveys/MASQ_raw.csv"
MASQ <-read.csv(MASQ.path, header = T) %>% select(BABS_ID, starts_with("MASQ")) %>%
  group_by(BABS_ID) %>% mutate_if(is.character, as.integer) %>% ungroup()
MASQ.output.path <- "~/Library/CloudStorage/Box-Box/BABS_Neuropsych/Data/MASQ_imputed_sum.csv"
```

## Optional: Participant IDs for summarization

```{r Sub_IDs, warning=FALSE, message=FALSE}
# Enter all participants that you would like to summarize here)
## This section can be commented out if you want to run all available participants
sub.IDs<- c("BABS005", "BABS006","BABS008", "BABS024", "BABS004", "BABS007", "BABS009", "BABS010", "BABS011", "BABS012")
```

## Cleaning data frame for summary

```{r MASQ_clean, warning=FALSE, message=FALSE}
#Creating clean data frame for summary
MASQ.clean <- MASQ %>% pivot_longer(names_to = "facet", values_to = "response", -c(BABS_ID, MASQ_Session)) %>%
  separate_wider_delim(facet,"__", names = c("Scale", "Item")) %>%
  separate_wider_delim(Scale,"_", names = c(NA, "Scale")) %>%
  mutate(Value = if_else(Scale == "AD", recode(response, "1" = 5, "2" = 4, "3" = 3, 
                          "4" = 2, "5" = 1), response)) %>%
  select(BABS_ID, MASQ_Session, Scale, Value)

#If you would like to create a summary using only a unique subset of participant IDs that you have supplied (in previous code chunk), you can simply add the following line of code to filter the raw data to the code above
# %>% filter(BABS_ID %in% sub.IDs)
```

## Counting the number of missing responses & imputing missing data
### Participants missing > 20% of their data for a given scale will be removed (threshold can be edited for your own purposes)
### Printed below are all participants with missing values ≤ 20%, on which imputation was carried out

```{r MASQ_impute, warning=FALSE, message=FALSE}
#creating data frame that summarizes the amount of missing data per (sub)scale for each participant
MASQ.missing.sum <- MASQ.clean %>% group_by(BABS_ID, MASQ_Session, Scale) %>%
  summarise(count.missing = sum(is.na(Value)),
            count.response = sum(!is.na(Value))) %>%
  mutate(total = count.missing + count.response,
         prop.missing = count.missing/total,
         flag.missing = if_else(prop.missing > 0.2, 1, 0)) %>%
  filter(flag.missing == 0)
MASQ.missing.sum.tbl <- MASQ.missing.sum %>% filter(prop.missing != 0)
#printing table with the missing data summary
kable(MASQ.missing.sum.tbl) %>% kable_styling()
#creating data frame with *only* participants who have acceptable amounts of missing data (i.e., < 20% missing)
MASQ.clean.IDs <- MASQ.missing.sum %>% ungroup() %>% select(BABS_ID, MASQ_Session) %>% group_by(BABS_ID, MASQ_Session) %>% distinct()
#New data frame with imputed data (using median of the subscale values)
MASQ.clean.imputed <- inner_join(MASQ.clean, MASQ.clean.IDs) %>% group_by(BABS_ID, MASQ_Session, Scale) %>%
  mutate(median_subscale = round(median(Value, na.rm = T), digits = 0),
         Imputed.Value = if_else(is.na(Value), median_subscale, Value)) %>% ungroup() %>%
  select(BABS_ID, MASQ_Session, Scale, Imputed.Value)
```

## Creating MASQ-Specific Summary Scores with Imputed Values

```{r MASQ_sum, warning=FALSE, message=FALSE}
#data frame with summary items
MASQ.sum <- MASQ.clean.imputed %>% group_by(BABS_ID, MASQ_Session, Scale) %>%
  summarise(Score = sum(Imputed.Value)) %>%
  pivot_wider(id_cols = c("BABS_ID", "MASQ_Session"), names_from = "Scale", values_from = "Score")
#to save the results, un-comment the line below; file path & name can be adjusted in the first code chunk
write.csv(MASQ.sum, file = MASQ.output.path, row.names = F)
```

### Descriptive summary of MASQ responses (imputed sample)

```{r MASQ_desc_sum, warning=FALSE, message=FALSE}
#counting the number of observations and summarizing mean & SD
MASQ.desc.sum <- MASQ.sum %>% describe() %>% select(-vars) %>% rownames_to_column(var = "Variable") %>%
  filter(Variable != "BABS_ID*") %>% filter(Variable != "MASQ_Session")

kable(MASQ.desc.sum, col.names = c("Variable","N","Mean","SD","Median","Trimmed Mean","Median Abs. Deviation","Min","Max","Range","Skew","Kurtosis","SE"),
      caption = "MASQ Summary Table") %>% kable_styling()
#creating long data frame
d.MASQ.long <- MASQ.sum %>% 
  pivot_longer(names_to = "Facet", values_to = "Score", -c(BABS_ID, MASQ_Session))
#plotting distribution of scores
p.MASQ <- ggplot(d.MASQ.long, aes(Score)) +
  geom_bar() + 
  labs(title = "MASQ Scores in BABS Sample") +
  theme_classic() + facet_wrap(.~ Facet)
p.MASQ
```
